My title

### 2024-11-03 paper/paper.qmd
ethics

@@

>>>>

Ethics-wise, the survey does a good job of informing individuals of the details of the survey, such as its purpose and how participants' data is to be used. Personally-identifiable data (i.e. name, phone number, etc.) is not collected during the survey other than to ensure that repeat numbers are not drawn, and the usage of live interviewers to conduct the survey ensures that concerns about the ethics of the survey can be voiced and answered on-the-spot. Combined with the lack of financial incentive for participants, which suggests that all participants participate of their complete free will and intention, this is an ethically sound methodology for conducting a political survey.

@@

Finally, how ethics are handled is a crucial part of any survey methodology. In this idealised methodology, consent will be asked for at the beginning of the survey, full disclosure of how information is used will be given beforehand and no self-identifiable information will be recorded (so no names, phone numbers, etc.). The $10 incentive is enough to hopefully make it worthwile for participants' time, but also not ideally not significant enough of an incentive to make individuals suppress otherwise deal-breaking concerns with the survey purely for the sake of the incentive.
